---
title       : Fone
subtitle    : Formula 1 results and locations
author      : rrunner
job         : Developing Data Products
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []   # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r, echo=FALSE}
# knitr settings
opts_chunk$set(cache=FALSE)
```


## Fone

- **Fone** is a simple shiny application that presents circuit location on a world map and race results in two separate tabs
- Receives two user inputs: Year and circuit

---

## Source data and API

> - **Fone** utilises the [Ergast API](http://ergast.com/mrd/)
> - Downloads data as JSON objects 
> - Convert to data frames before display 

---

## Race locations

- Race locations are displayed in the first tab
- The current selected circuit is marked red on the world map

```{r worldmap, echo=FALSE, fig.width=12, fig.height=6}
suppressPackageStartupMessages(library(ggplot2))
load("races.RData")
map_theme <- theme(axis.line = element_blank(),
                   axis.text = element_blank(),
                   axis.ticks = element_blank(),
                   axis.title = element_blank(),
                   panel.grid = element_blank(),
                   panel.background = element_rect(fill = "lightsteelblue"))

m <- ggplot() + coord_cartesian(ylim=c(-60, 70), xlim=c(-150, 180)) + borders(database="world", colour="grey", fill="darkseagreen") + geom_point(data=local_data, aes(long, lat), color="black", size=2) + map_theme

print(m + geom_point(data=local_data[1, c("long", "lat")],
                     aes(long, lat), color="red", size=2))
```


---

## Race results

- Results are listed in the second tab
- For example, the podium finishers at the Melbourne 2014 race are:

```{r, echo=FALSE, results='asis'}
library(xtable)
load("results.RData")
print(xtable(results[1:3, ]), type="html")
```
